Tree establishment in models of forest dynamics: a key priority for further research

### 2023-04-26 manuscript/manuscriptRW.Rmd
clean code lines in manuscript

```{r, echo=FALSE}
  # devtools::install_github("cboettig/knitcitations@v1")
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries = FALSE)
  library(bibtex)
  options(tinytex.verbose = TRUE)
  #knitr::opts_chunk$set(echo = TRUE, fig.pos = "h", out.extra = "")

```

>>>>

```{r, echo=FALSE}
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries = FALSE)
  library(bibtex)
  options(tinytex.verbose = TRUE)
```
